Finite element analysis ofmulti-dimensional and simplifiedmodels for beams and plates

### 2023-11-29 files/Chapter3/femconvergence.tex
chapter 3

\subsubsection*{Problem E}
Find a vector $u \in V$ and number $\lambda \in R$ such that $u \neq 0$ and
\begin{equation}
	b(u,v) = \lambda (u,v) \label{GEVP}
\end{equation} for each $v \in V$.

@@

Consider the Galerkin approximation for \eqref{GEVP}:
\subsubsection*{Problem $E^h$}
Find $u^h \in S^h$ such that $u^h \neq 0$ and \[b(u^h, v) = \lambda^h(u^h,v) \textrm{ for all } v \in S^h.\]

@@

The pair $(\lambda^n, \bar{u}_n)$ correspond to the pair $(\lambda^h_k, u^h_k)$ which is the solution of Problem $E^h$. It is necessary to some of the teory to make the connection.

@@

The elements $Pu_j$ are the projections of the eigenfunctions $u_j$ into the space $S^h$. These projections $Pu_j$ are not necessarily equal to $u^h \in S^h$. In fact, $u^h_j$  can be vastly different from $u_j$. The situation is not simple. It is possible that $Py_k = 0$ for large $k$ Assume that the dimension of $S^h$ is large enough, substantially larger than $m$.

@@

	Now we take an arbitrary $v \in S_{m}$, $v \neq 0$. Then there exists a $u \in E_{m}$ such that $Py = v$. This $Py$ is the projection into $S_m$ of some $u \in E_m$ (which is also $\displaystyle \frac{1}{||u||_{W}}u \in B_m$).

@@

	From the Rayleigh-Ritz Projection, $Pu$ is the closest element in $S^h$ to $u$. In particular, $||u-Pu||_{W}\leq ||u-\Pi u||_{W}$, where $\Pi u$ is the interpolation of $u$ into $S^h$.

@@

Therefore t $||u_{m} -  u_{m}^{h}||_{W} \leq Ch^{k}||u^{k}||_{W}$. So for any $\epsilon >0$ , a $\delta >0$ can be found such that if $h < \delta$, $||u_{m} -  u_{m}^{h}||_{W} < \epsilon$.

>>>>

\subsubsection*{Problem E}
Find a vector $u \in V$ and number $\lambda \in R$ such that $u \neq 0$ and
\begin{equation}
	b(u,v) = \lambda c(u,v) \label{GEVP}
\end{equation} for each $v \in V$.

@@

Consider the Galerkin approximation for \eqref{GEVP}:
\subsubsection*{Problem $E^h$}
Find $u^h \in S^h$ such that $u^h \neq 0$ and \[b(u^h, v) = \lambda^h c(u^h,v) \textrm{ for all } v \in S^h.\]

@@

The pair $(\lambda^n, \bar{u}_n)$ correspond to the pair $(\lambda^h_k, u^h_k)$ which is the solution of Problem $E^h$. It is necessary to some of the theory to make the connection.

@@

The elements $Pu_j$ are the projections of the eigenfunctions $u_j$ into the space $S^h$. These projections $Pu_j$ are not necessarily equal to $u^h \in S^h$. In fact, $u^h_j$  can be vastly different from $u_j$. The situation is not simple. It is possible that $Pu_k = 0$ for large $k$ Assume that the dimension of $S^h$ is large enough, substantially larger than $m$.

@@

	Now we take an arbitrary $v \in S_{m}$, $v \neq 0$. Then there exists a $u \in E_{m}$ such that $Pu = v$. This $Pu$ is the projection into $S_m$ of some $u \in E_m$ (which is also $\displaystyle \frac{1}{||u||_{W}}u \in B_m$).

@@

	$Pu$ is the closest element in $S^h$ to $u$. In particular, $||u-Pu||_{W}\leq ||u-\Pi u||_{W}$, where $\Pi u$ is the interpolation of $u$ into $S^h$.

@@

Therefore $||u_{m} -  u_{m}^{h}||_{W} \leq Ch^{k}||u^{k}||_{W}$. So for any $\epsilon >0$ , a $\delta >0$ can be found such that if $h < \delta$, $||u_{m} -  u_{m}^{h}||_{W} < \epsilon$.
